---
title: "Exercise 5 - A reproducible workflow in rmarkdown"
name: Rick
output: html_document
---
```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(magrittr)
```

---

### Sample 100 samples (n = 10) from a standard normal distribution.
```{r}
#empty container
samples <- matrix(NA, 10, 100)

#100 sample met n=10
for (i in 1:100){
samples[,i] <- rnorm(10, mean=0, sd=1)
}

#First five samples
samples[1:10, 1:5]
```

---

### For each of these samples, calculate the following statistics for the mean:

$Bias = \mu - \bar{x}$

$Standard \: error = \frac{s}{\sqrt{n}}$

$Confidence \: intervals = \mu \pm SE * 1.96$


```{r}
#population mean
popmean <- 0

#sample means
sample_means <- apply(samples, 2, mean)
sample_sd <- apply(samples, 2, sd)

#absolute bias
bias <- sample_means - popmean

#standard error of the mean = standard deviation of the sampling distribution
SE <- sample_sd/ sqrt(10)

#lower bound 95% CI
CI_low <- sample_means - (1.96 * SE)
CI_high <- sample_means + (1.96 * SE)

#create one dataframe
df <- as.data.frame(cbind(samplenr = 1:100,sample_means, CI_low, CI_high))

head(df)
```

---

### Create a plot that demonstrates the following:

***“A replication of the procedure that generates a 95% confidence interval that is centered around the sample mean would cover the population value at least 95 out of 100 times”*** (Neyman, 1934)


```{r, warning=FALSE, echo=FALSE, message=FALSE}
require(ggplot2)
ggplot(df, aes(x = samplenr, y = sample_means)) +
  geom_point(size = 1) +
  geom_errorbar(aes(ymax = CI_low, ymin = CI_high)) + geom_hline(yintercept=popmean, col="blue")
```

---

These are the samples with samples means that fall outside the confidence intervals.
```{r}
df[popmean > CI_high | popmean < CI_low,]
```

---


